Air Quality and CMS Data

### 2021-01-29 code/data-processors/cms-data-processor.Rmd
added SE to all datasets - created config file for fac-EM runs- cleaned outputs- plot outputs

```{r PMC Residual}
cmp.sub <- c("PM_AS","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")

@@

```{r PMC race}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.raceA <- dt.ndi.pmc.raceA %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rA, everything())

@@

dt.ndi.pmc.raceB <- dt.ndi.pmc.raceB %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rB, everything())

@@

dt.ndi.pmc.raceH <- dt.ndi.pmc.raceH %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rH, everything())

@@

dt.ndi.pmc.raceW <- dt.ndi.pmc.raceW %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

@@

```{r PMC urbanicity}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.urban <- dt.ndi.pmc.urban %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, urb, everything())

@@

dt.ndi.pmc.rural <- dt.ndi.pmc.rural %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rur, everything())

@@

cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.urban.sesL <- dt.ndi.pmc.urban.ses %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesL, everything())

@@

dt.ndi.pmc.urban.sesM <- dt.ndi.pmc.urban.ses %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesM, everything())

@@

dt.ndi.pmc.urban.sesH <- dt.ndi.pmc.urban.ses %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesH, everything())

@@

```{r PMC Region}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.west <- dt.ndi.pmc.west %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

@@

dt.ndi.pmc.midwest <- dt.ndi.pmc.midwest %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rMW, everything())

@@

dt.ndi.pmc.south <- dt.ndi.pmc.south %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rS, everything())

@@

dt.ndi.pmc.northeast <- dt.ndi.pmc.northeast %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rNE, everything())

@@

```{r PMC Age}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aLE75, everything())

@@

dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aM75, everything())

@@

```{r PMC Sex}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

### Female
dt.ndi.pmc.sexF <- dt.sex %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  mutate(sexF = ifelse(sex == "F", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexF, everything())

@@

### Male
dt.ndi.pmc.sexM <- dt.sex %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  mutate(sexM = ifelse(sex == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexM, everything())

@@

```{r PMC BRFSS}
dt.pmc <- dt.pmc.1yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC BZ 6}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC BZ 12}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC BZ 24}
cmp.sub <- c("AS", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 5yr}
dt.pmc <- dt.pmc.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc, 
          file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
          row.names = F)
```

```{r PMC - 4yr - 5yr}
dt.pmc <- dt.pmc.4yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc, 
          file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 3yr - 5yr}
dt.pmc <- dt.pmc.3yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc, 
          file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 2yr - 5yr}
dt.pmc <- dt.pmc.2yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc, 
          file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 1yr - 5yr}
dt.pmc <- dt.pmc.1yr.5yr %>% 
  rename_at(vars(AS:ZN), ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc, 
          file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),
          row.names = F)
```

>>>>

```{r PMC Residual}
cmp.sub <- c("PM_SE","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")

@@

```{r PMC race}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.raceA <- dt.ndi.pmc.raceA %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rA, everything())

@@

dt.ndi.pmc.raceB <- dt.ndi.pmc.raceB %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rB, everything())

@@

dt.ndi.pmc.raceH <- dt.ndi.pmc.raceH %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rH, everything())

@@

dt.ndi.pmc.raceW <- dt.ndi.pmc.raceW %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

@@

```{r PMC urbanicity}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.urban <- dt.ndi.pmc.urban %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, urb, everything())

@@

dt.ndi.pmc.rural <- dt.ndi.pmc.rural %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rur, everything())

@@

cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.urban.sesL <- dt.ndi.pmc.urban.ses %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesL, everything())

@@

dt.ndi.pmc.urban.sesM <- dt.ndi.pmc.urban.ses %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesM, everything())

@@

dt.ndi.pmc.urban.sesH <- dt.ndi.pmc.urban.ses %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sesH, everything())

@@

```{r PMC Region}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.west <- dt.ndi.pmc.west %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

@@

dt.ndi.pmc.midwest <- dt.ndi.pmc.midwest %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rMW, everything())

@@

dt.ndi.pmc.south <- dt.ndi.pmc.south %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rS, everything())

@@

dt.ndi.pmc.northeast <- dt.ndi.pmc.northeast %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rNE, everything())

@@

```{r PMC Residual Region}
cmp.sub <- c("PM_SE","PM_CA","PM_CL","PM_NA","PM_NI","PM_NO3",
            "PM_OC","PM_PB","PM_SI","PM_SO4","PM_V","PM_ZN")

### West = 1
dt.ndi.pmc.west <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rW = ifelse(Region.IV == 1, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

dt.ndi.pmc.res.west <- dt.ndi.pmc.west %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

write.csv(dt.ndi.pmc.res.west, 
          file = here('data', 'processed', 'ndi-pmc-res-west.csv'),
          row.names = F)

### Midwest = 2

dt.ndi.pmc.midwest <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rMW = ifelse(Region.IV == 2, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

dt.ndi.pmc.res.midwest <- dt.ndi.pmc.midwest %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rMW, everything())

write.csv(dt.ndi.pmc.res.midwest, 
          file = here('data', 'processed', 'ndi-pmc-res-midwest.csv'),
          row.names = F)

### South = 3

dt.ndi.pmc.south <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rS = ifelse(Region.IV == 3, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

dt.ndi.pmc.res.south <- dt.ndi.pmc.south %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rS, everything())

write.csv(dt.ndi.pmc.res.south, 
          file = here('data', 'processed', 'ndi-pmc-res-south.csv'),
          row.names = F)

### Northeast = 4

dt.ndi.pmc.northeast <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rNE = ifelse(Region.IV == 4, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

dt.ndi.pmc.res.northeast <- dt.ndi.pmc.northeast %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rNE, everything())

write.csv(dt.ndi.pmc.res.northeast, 
          file = here('data', 'processed', 'ndi-pmc-res-northeast.csv'),
          row.names = F)

```

```{r PMC Age}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

dt.ndi.pmc.ageLE75 <- dt.ndi.pmc.ageLE75 %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aLE75, everything())

@@

dt.ndi.pmc.ageM75 <- dt.ndi.pmc.ageM75 %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aM75, everything())

@@

```{r Factor Age}
fac <- c("Factor1","Factor2","Factor3","Factor4",
         "Factor5","Factor6","Factor7","Factor8")

### Age 
dt.age <- dt.master.ndi.pmc %>%
  mutate(age = ifelse(age <= 75, "LE", "M")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

### LE 75
dt.ndi.fac.ageLE75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aLE75 = ifelse(age == "LE", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

for (cmp in fac){
    dt.ndi.fac.ageLE75[ ,paste0("aLE75_",cmp)] <- 
      dt.ndi.fac.ageLE75[ ,cmp] * dt.ndi.fac.ageLE75$aLE75
}

dt.ndi.fac.ageLE75 <- dt.ndi.fac.ageLE75 %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aLE75, everything())

write.csv(dt.ndi.fac.ageLE75, 
          file = here('data', 'processed', 'ndi-fac-ageLE75.csv'),
          row.names = F)

### M 75
dt.ndi.fac.ageM75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aM75 = ifelse(age == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

for (cmp in fac){
    dt.ndi.fac.ageM75[ ,paste0("aM75_",cmp)] <- 
      dt.ndi.fac.ageM75[ ,cmp] * dt.ndi.fac.ageM75$aM75
}

dt.ndi.fac.ageM75 <- dt.ndi.fac.ageM75 %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, aM75, everything())

write.csv(dt.ndi.fac.ageM75, 
          file = here('data', 'processed', 'ndi-fac-ageM75.csv'),
          row.names = F)
```

```{r PMC Sex}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

@@

### Female
dt.ndi.pmc.sexF <- dt.sex %>% 
  mutate(sexF = ifelse(sex == "F", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.pmc.sexF <- dt.ndi.pmc.sexF %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexF, everything())

@@

### Male
dt.ndi.pmc.sexM <- dt.sex %>% 
  mutate(sexM = ifelse(sex == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.ndi.pmc.sexM <- dt.ndi.pmc.sexM %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_")) %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexM, everything())

@@

```{r Factor Sex}
fac <- c("Factor1","Factor2","Factor3","Factor4",
         "Factor5","Factor6","Factor7","Factor8")

dt.sex <- dt.master.ndi.pmc %>% 
    select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses)

### Female
dt.ndi.fac.sexF <- dt.sex %>% 
  mutate(sexF = ifelse(sex == "F", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

for (cmp in fac){
    dt.ndi.fac.sexF[ ,paste0("sexF_",cmp)] <- 
      dt.ndi.fac.sexF[ ,cmp] * dt.ndi.fac.sexF$sexF
}

dt.ndi.fac.sexF <- dt.ndi.fac.sexF %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexF, everything())

write.csv(dt.ndi.fac.sexF, 
          file = here('data', 'processed', 'ndi-fac-sexF.csv'),
          row.names = F)

### Male
dt.ndi.fac.sexM <- dt.sex %>% 
  mutate(sexM = ifelse(sex == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

for (cmp in fac){
    dt.ndi.fac.sexM[ ,paste0("sexM_",cmp)] <- 
      dt.ndi.fac.sexM[ ,cmp] * dt.ndi.fac.sexM$sexM
}

dt.ndi.fac.sexM <- dt.ndi.fac.sexM %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, sexM, everything())

write.csv(dt.ndi.fac.sexM, 
          file = here('data', 'processed', 'ndi-fac-sexM.csv'),
          row.names = F)
```

```{r PMC BRFSS}
dt.pmc <- dt.pmc.1yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

```{r Factor BRFSS}
dt.ses <- dt.ses.site.bz12 %>% 
  mutate(ses = SES.Zip.Norm) %>% 
  select(Site.ID, Year, ses)

dt.ndi.fac.brfss <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.brfss.site) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.fac.brfss, 
          file = here('data', 'processed', 'ndi-fac-brfss.csv'),
          row.names = F)
```

```{r PMC BZ 6}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

```{r PMC BZ 12}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

```{r PMC BZ 24}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  select(Site.ID, Year, Month, cmp.sub) %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

```{r PMC - 5yr}
dt.pmc <- dt.pmc.5yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

dt.ndi.pmc.5 <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.5, 
          file = here('data', 'processed', 'ndi-pmc-5yr.csv'),
          row.names = F)
```

```{r PMC - 4yr - 5yr}
dt.pmc <- dt.pmc.4yr.5yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

dt.ndi.pmc.4 <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.4, 
          file = here('data', 'processed', 'ndi-pmc-4yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 3yr - 5yr}
dt.pmc <- dt.pmc.3yr.5yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

dt.ndi.pmc.3 <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.3, 
          file = here('data', 'processed', 'ndi-pmc-3yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 2yr - 5yr}
dt.pmc <- dt.pmc.2yr.5yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

dt.ndi.pmc.2 <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.2, 
          file = here('data', 'processed', 'ndi-pmc-2yr-5yr.csv'),
          row.names = F)
```

```{r PMC - 1yr - 5yr}
dt.pmc <- dt.pmc.1yr.5yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

dt.ndi.pmc.1 <- dt.master.ndi.pmc %>% 
  mutate(StrID = paste(age, sex, race)) %>% 
  select(Site.ID, Year, Month, StrID, no_enrollee:no_death_kidn) %>%  
  inner_join(dt.pmc) %>% 
  inner_join(dt.ses) %>% 
  rename(SiteID = Site.ID)

write.csv(dt.ndi.pmc.1, 
          file = here('data', 'processed', 'ndi-pmc-1yr-5yr.csv'),
          row.names = F)
```
